---
title: "Alcohol vs Seat choice"
author: "Emma"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
 
  The visual on the back is quite a bit different from the middle, and the plot shows an even bigger difference from the back and the front row. 
  
## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
According to the box plot, the back row drinks 8.5 drinks a week, making this row the highest group of drinkers out of the three categories. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value represents the chance of obtaining a result like we just got, if the null hypothesis is actually true. Since the result is so small, I myself am rejecting the null hypothesis.
```{r}
plot(TukeyHSD(model1))
```

We now need to look and see if we can discover what is different from eachother. The front and back are slightly different from eachother. But the front and middle, and the back and middle are extremley different from eachother as you can see from the mean values in the plot.

## Conclusions


